% !TeX root = document.tex
% !TeX program = lualatex

\input{preamble}

\newcommand{\crule}{\par\noindent\rule{\textwidth}{0.5pt}}

\begin{document}
\thispagestyle{empty}

\begin{center}
	\LARGE \textbf{Vladyslav Rehan}\\[4mm] \normalsize
	\texttt{\phonenumber{+380636637248} \(\diamond\)\
	\href{mailto:rehanvladyslav@gmail.com}{rehanvladyslav@gmail.com} \(\diamond\)
	\url{https://github.com/Dolfost}}
\end{center}
\crule
\section{Education}
\textbf{Applied mathematics and software} | Bachelor's degree, 3rd year | \href{http://nau.edu.ua/en/}{Kyiv Aviation Institute}\\
Less-or-more important works included:
\begin{itemize}
	\item Statistical approach to detecting rare fragments on a digital image
	\item Automated software for multidimensional data analysis
\end{itemize}

\crule
\section{About myself}
Can fluently read books and documentation in english. Worked with Github
Actions, have basic FreeCAD usage experience. Primarily write on C++. A lot of
knowlede about programming and associated tools was gathered from
\href{https://github.com/Dolfost/Dolfost/blob/main/README.md#literature--sources}{books}.
Use LaTeX (lualatex) as daily driver for university reports.

\crule
\section{Work experience}
I have no work experience.

\section{Skills}
\begin{itemize}
	\item C/C++, CMake, Bash, Lua, LaTeX
	\item Git, Doxygen
\end{itemize}
C++ libraries: STL, Qt6, ExprTk, QCustomPlot, libpng, tomlplusplus

\section{Tools}
Maily use \href{https://github.com//Dolfost/dotfiles}{configured} tmux, nvim,
lldb, *nix command line tools combo. Have some year-old week-long experience in
QtCreator that was gained before moving to full CMake-only Qt workflow. I have
understating of CTest unit testing and CPack packaging semantics. Regularry use
remote shell acess technologies like ssh and scp(or better -- rsync). Own a
local headless linux machine that is avaliable from WAN.

\section{One-man projects}
\begin{itemize}
	\item \href{https://github.com/Dolfost/matstat}{Multidimensional data analysis software} (C++, Qt, QCustomPlot, ExprTk, \(\approx 12\)k lines)
	\item \href{https://github.com/Dolfost/tartan}{Chess game backend} (C++, CI/CD, Doxygen, CTest, CPack)
	\item \href{https://github.com/Dolfost/ssmk/tree/develop}{.png spritesheet factory} (C++, libpng, tomlplusplus)
	\item \href{https://github.com/Dolfost/calgo}{Numerical methods library} (C++, CI/CD, Qt, Doxygen) 
	\item \href{https://github.com/Dolfost/snake-cpp}{nCurses snake game} (C/C++, newcurses textual user interface)
\end{itemize}

\vfill{}

\begin{center}
	\tiny \href{\lrthomepage}{git ver. \lrtversion}
\end{center}

\end{document}
